Gravitational-wave sensitivity curves

### 2014-10-02 V2/Detectors.tex

The next great advancement in radio astronomy shall come with the completion of the Square Kilometre Array \citep[SKA;][]{Dewdney2009}. This shall greatly increase the sensitivity of pulsar timing \citep{Kramer2004}. The sensitivity curves plotted in \ref{app:a} for the SKA assumes $50$ pulsars timed every 2 weeks for 20 years with an r.m.s.\ error in each timing residual of $30\,\textrm{ns}$. Our choice of 50 pulsars might be conservative, it is possible that the SKA will discover many more suitable milli-second pulsars than this throughout its operation, in which case the corresponding sensitivity curve would become lower.

>>>>

The next great advancement in radio astronomy shall come with the completion of the Square Kilometre Array \citep[SKA;][]{Dewdney2009}. This shall greatly increase the sensitivity of pulsar timing \citep{Kramer2004}. The sensitivity curves plotted in \ref{app:a} for the SKA assumes $50$ pulsars timed every 2 weeks for 20 years with an r.m.s.\ error in each timing residual of $30~\textrm{ns}$. Our choice of 50 pulsars might be conservative, it is possible that the SKA will discover many more suitable milli-second pulsars than this throughout its operation, in which case the corresponding sensitivity curve would become lower.
